\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-07-22 tex/overview.tex
fix typo

We would like to determine whether selection for dynamical robustness would result in a preference for the maintenance of one kind of network architecture relative to another. In order to then classify the properties of this process according to network architecture, we consider cases where the condition $\adj(G_A) = \adj(G_{A'})$ holds, which results in an analogous processes defined on each $G$-class $[G] \in \mathcal{F}/G$ given by
$$
P([A]^T \mid G_A {=} G) = \sum_{ \{ f^T \mid f_i^T \in [A]_i^T \} } P(f^T)
$$
for each history of length $T$, $[A]^T = ( [A_1], [A_2], \ldots, [A_T] ) \in [G]^T$
as visualized in \ref{fig:robustnessprocess}C. This now corresponds to a collection of ensembles of dynamical systems each with equivalent connectivities corresponding to a graph $G$. For each graph, there is a potentially different value of robustness given by
\begin{equation}\label{eq:robustnessbygraph}
\begin{aligned}
R(G,S,\mu,\tau)  =
 \frac{\int\limits_{A,A' \in \mathbb{R}^{n \times n} \atop G_A = G} d\mu(A) d\tau(A' \mid A) \mathcal{S}(A) \mathcal{S}(A')}{\int\limits_{A \in \mathbb{R}^{n \times n} \atop G_A = G} d\mu(A) \mathcal{S}(A)}.
\end{aligned}
\end{equation}
Comparing the values of $R$ for each $G$-class in $\mathcal{F}/G$ places a partial ordering on network architectures, $G$, which allows for the determination of which network architectures would be expected to be enriched relative to others in an evolutionary process where selection is imposed in a manner that results in a bias toward higher $R$ values.

>>>>

We would like to determine whether selection for dynamical robustness would result in a preference for the maintenance of one kind of network architecture relative to another. In order to then classify the properties of this process according to network architecture, we consider cases where the condition $\adj(G_A) = \adj(G_{A'})$ holds, which results in analogous processes defined on each $G$-class $[G] \in \mathcal{F}/G$ given by
$$
P([A]^T \mid G_A {=} G) = \sum_{ \{ f^T \mid f_i^T \in [A]_i^T \} } P(f^T)
$$
for each history of length $T$, $[A]^T = ( [A_1], [A_2], \ldots, [A_T] ) \in [G]^T$
as visualized in \ref{fig:robustnessprocess}C. This now corresponds to a collection of ensembles of dynamical systems each with equivalent connectivities corresponding to a graph $G$. For each graph, there is a potentially different value of robustness given by
\begin{equation}\label{eq:robustnessbygraph}
\begin{aligned}
R(G,S,\mu,\tau)  =
 \frac{\int\limits_{A,A' \in \mathbb{R}^{n \times n} \atop G_A = G} d\mu(A) d\tau(A' \mid A) \mathcal{S}(A) \mathcal{S}(A')}{\int\limits_{A \in \mathbb{R}^{n \times n} \atop G_A = G} d\mu(A) \mathcal{S}(A)}.
\end{aligned}
\end{equation}
Comparing the values of $R$ for each $G$-class in $\mathcal{F}/G$ places a partial ordering on network architectures, $G$, which allows for the determination of which network architectures would be expected to be enriched relative to others in an evolutionary process where selection is imposed in a manner that results in a bias toward higher $R$ values.
